Denotational Semantics of Gradual Typing using Synthetic Guarded Domain Theory

### 2024-07-12 paper-new/discussion.tex
fix an error

A line of work by New, Licata and Ahmed proves graduality by
interpreting type precision $c : A \ltdyn A'$ as an
\emph{embedding-projection pair}, that is a pure function $e : A \to
A'$ and a possibly erroring projection $p : \li A' \multimap \li A$
such that $p \circ e = \id$ and $e \circ p \ltdyn \id$
\cite{newahmed,newlicata,newlicataahmed}. At first glance, our model
of precision looks somewhat different: it is a \emph{relation}
$\sem{c} : A \relto A'$ with a quasi-representability structure that
gives us something like $e$ and $p$ in an embedding-projection
pair. The relationship between these models is that \emph{if} the
relation were \emph{truly} representable rather than only
quasi-representable we would have that $e$ and $p$ form a \emph{Galois
connection} $e \circ p \ltdyn \id$ and $\id \ltdyn p \circ
e$. However, we have dropped the stronger property of retraction from
our analysis in this work. With true representability, the relation
$c$ is \emph{uniquely determined} by the embedding $e$, but since we
only have quasi-representability, we need to keep the relation around
explicitly. So the extra complexity of managing explicit relations is
a cost of the intensional reasoning that guarded type theory
introduces.

>>>>

A line of work by New, Licata and Ahmed proves graduality by
interpreting type precision $c : A \ltdyn A'$ as an
\emph{embedding-projection pair}, that is a pure function $e : A \to
A'$ and a possibly erroring projection $p : \li A' \multimap \li A$
such that $p \circ e = \id$ and $e \circ p \ltdyn \id$
\cite{newahmed,newlicata,newlicataahmed}. At first glance, our model
of precision looks somewhat different: it is a \emph{relation}
$\sem{c} : A \rel A'$ with a quasi-representability structure that
gives us something like $e$ and $p$ in an embedding-projection
pair. The relationship between these models is that \emph{if} the
relation were \emph{truly} representable rather than only
quasi-representable we would have that $e$ and $p$ form a \emph{Galois
connection} $e \circ p \ltdyn \id$ and $\id \ltdyn p \circ
e$. However, we have dropped the stronger property of retraction from
our analysis in this work. With true representability, the relation
$c$ is \emph{uniquely determined} by the embedding $e$, but since we
only have quasi-representability, we need to keep the relation around
explicitly. So the extra complexity of managing explicit relations is
a cost of the intensional reasoning that guarded type theory
introduces.
